---
title: "Document dimension analysis"
author: "`r author`"
date: "`r Sys.Date()`"
output: markdown_document
---


## Average document dimensions 

```{r docsizes-1, echo=FALSE, message=FALSE, warning=FALSE}
# only include gatherings with sufficiently many documents
df1 <- filter(df, !is.na(gatherings.original) & (!is.na(height.original) | !is.na(width.original))) %>%
       filter(!gatherings.original == "NA") %>%       
       group_by(gatherings.original, publication_country) %>% 
       summarize(n = n())

# Gatherings x countries title counts
library(reshape2)
tab <- acast(df1, gatherings.original ~ publication_country, fill = 0)
tab <- cbind(tab, total = rowSums(tab))
```


We have `r sum(tab)` documents with publication country and original gatherings information. We have `r sum(!df$gatherings.original == "NA")` documents with original gatherings information but no publication country information.

```{r docsizes-2, echo=FALSE, message=FALSE, warning=FALSE}
kable(tab, caption = "Gatherings x countries title counts")
```



### Selected gatherings across time; by publication country

```{r docsizes-3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=5}

nmin <- 2000
top.gatherings <- setdiff(names(which(table(df$gatherings.original) > nmin)), "NA")

df2 <- filter(df, !is.na(gatherings.original) & (!is.na(height.original) | !is.na(width.original))) %>%
       filter(gatherings.original %in% top.gatherings) %>%
       select(publication_decade, gatherings.original, height.original, width.original, publication_country)
       
df3 <- df2 %>% group_by(gatherings.original, publication_decade, publication_country) %>% 
       summarize(mean.height.original = mean(height.original, na.rm = T),
    	         mean.width.original  = mean(width.original, na.rm = T),
		 n = n())

# Select specific gatherings
for (sel.gatherings in top.gatherings) {
  # .. and countries that have enough docs ..
  top.countries <- names(which(sort(sapply(split(df3$n, df3$publication_country), sum)) > 100))
  mydf <- df3 %>% filter(gatherings.original == sel.gatherings & publication_country %in% top.countries)
  p <- ggplot()
  p <- p + geom_point(data = mydf, aes(x = publication_decade, y = mean.height.original, size = n, group = publication_country, color = publication_country))
  p <- p + geom_smooth(data = mydf, method = "loess", aes(x = publication_decade, y = mean.height.original, color = publication_country))
  p <- p + ggtitle(paste(sel.gatherings, ": height"))
  print(p)
}
```


### Average document sizes 

Only cases with `r nmin` documents are shown:

```{r docsizes-4, echo=FALSE, message=FALSE, warning=FALSE}
df2 <- filter(df, !is.na(gatherings.original) & (!is.na(height.original) | !is.na(width.original))) %>%
       filter(gatherings.original %in% top.gatherings) %>%
       group_by(gatherings.original) %>% 
       summarize(mean.height = mean(height.original, na.rm = T),
	    median.height = mean(height.original, na.rm = T),
    	    mean.width = mean(width.original, na.rm = T), 
	    median.width = mean(width.original, na.rm = T), 
	    n = n())

mean.dimensions <- as.data.frame(df2)
kable(mean.dimensions, caption = "Average document dimensions")
```



### Average document sizes by decade and publication country

Only cases with `r nmin` documents are shown:

```{r docsizes-5, echo=FALSE, message=FALSE, warning=FALSE}
df2 <- filter(df, !is.na(gatherings.original) & (!is.na(height.original) | !is.na(width.original))) %>%
       filter(gatherings.original %in% top.gatherings) %>%
       group_by(gatherings.original, publication_country, publication_decade) %>% 
       summarize(mean.height = mean(height.original, na.rm = T),
	    median.height = mean(height.original, na.rm = T),
    	    mean.width = mean(width.original, na.rm = T), 
	    median.width = mean(width.original, na.rm = T), 
	    n = n())

mean.dimensions <- as.data.frame(df2)
kable(mean.dimensions, caption = "Average document dimensions")
```

